Full Title of Article\titlebreak This Title Has A Line Break

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
first 2 models drafted

% Authors
\if0\blind {
    \title {
        \bf Title
    }

    \author {
        Author 1 \\
        Department of YYY, University of XXX\\
        and \\
        Author 2 \\
        Department of ZZZ, University of WWW
    }

    \maketitle
} \fi

% TOC
\newpage
    \tableofcontents
\newpage

% Abstract
\section{Abstract}

\input{sections/abstract}

% Introduction
\section{Introduction}
	\subsection{Background}

	\subsection{Related Work}

% Methodology
\section{Methodology}
	\subsection{Acquisition of Data}
	\tab Our gold-standard dataset consisted of 16K sampled patients with APOE gene <insert info about Biobank>. Each patient's EHR record was reviewed by an expert clinician (neurologist, psychiatrist, or geriatric psychiatrist) to annotate patients with presence, absence, or inconclusiveness of cognitive impairment.

	\subsection{Preprocessing}
	\tab We first created a list of keywords related to cognitive impairment (full list with frequency matches in Appendix A). For each patient in the BioBank data repository (mentioned above), we extracted all sequences containing any of the keywords. Several preprocessing steps were completed to increase the sequences to 800 characters minimum (more details in Appendix B) to allow for annotators to have more context when evaluating sequences.The preprocessed sequences were used as input for all models.

	% \subsubsection{Obtaining Gold Standard Labels} Fair Header (where you would talk about SLAT)

	\subsection{Machine Learning Models}
		% \subsubsection{TFIDF Vectors} Fair Header

	\subsection{Deep Learning Model}
		% \subsubsection{BERT and Transformers} Fair Header

% Results
\section{Results}
	\subsection{Model Results and Comparison}

% Conclusion
\section{Conclusion}

% Future Work
\section{Future Work}

% References
\section{References}

\section{Appendix A}

\begin{table*}[htbp]

	{
		\begin{tabular}{c|c|c}
		\toprule
	    \textbf{Rank} & \textbf{Keyword} & \textbf{Match Count} \\
	    \midrule

		1 & \textbf{Memory} & 109218 \\ 
		2 & \textbf{Cognition}  & 87655 \\ 
		3 & \textbf{Dementia} & 51034 \\ 
		4 & \textbf{Cerebral} &  45886 \\ 
		5 & \textbf{Cerebrovascular} & 36370 \\ 
		6 & \textbf{Cerebellar} & 26863 \\
		7 & \textbf{Cognitive Impairment} & 20267 \\ 
		8 & \textbf{Alzheimer} & 20581 \\ 
		9 & \textbf{MOCA} & 9767 \\ 
		10 & \textbf{Neurocognitive} & 7711 \\ 
		11 & \textbf{MCI} & 3889 \\ 
		12 & \textbf{Amnesia} & 3695 \\ 
		13 & \textbf{AD} & 2673 \\ 
		14 & \textbf{Lewy} & 2561 \\ 
		15 & \textbf{MMSE} & 2134 \\ 
		16 & \textbf{LBD} & 224 \\ 
		17 & \textbf{Corticobasal} & 147 \\ 
		18 & \textbf{Pick's} & 41 \\

	    \bottomrule
		\end{tabular}
	}
	{\caption{Keywords indicative of Cognitive Impairment}}

\end{table*}

\section{Appendix B}

>>>>

\maketitle

\begin{abstract}
\tab Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide. Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed. Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.  Information relevant to cognitive impairment is often found within electronic health records but manual review of clinician notes by experts is both time consuming and often prone to errors. Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data. 
\end{abstract}
\begin{keywords}
EHR, NLP, Demetia
\end{keywords}

\section{Introduction}
\label{sec:intro}

\section{Related Works}
\label{sec:RelatedWorks}

\section{Dataset, Preprocessing, and Annotations}

\paragraph{Dataset}
\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N=16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype data available from the BioBank. Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.

\paragraph{Preprocessing}
\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (listed in Table 1), and constructed 800 character sequences from the note text around each of these matches. Our cohort of 16,428 patients had 279,224 sequences in total.

\begin{table*}[htbp]
\floatconts
  {tab:operatornames}
  {\caption{Keywords indicative of Cognitive Impairment}}%
    {
        \begin{tabular}{lcc}
            \toprule
            \bfseries Keyword & \bfseries Match Count \\
            \midrule

            \textbf{Memory} & \fseries 109218 \\ 
            \textbf{Cognition}  & \fseries 87655 \\ 
            \textbf{Dementia} & \fseries 51034 \\ 
            \textbf{Cerebral} & \fseries 45886 \\ 
            \textbf{Cerebrovascular} & \fseries 36370 \\ 
            \textbf{Cerebellar} & \fseries 26863 \\
            \textbf{Cognitive Impairment} & \fseries 20267 \\ 
            \textbf{Alzheimer} & \fseries 20581 \\ 
            \textbf{MOCA} & \fseries 9767 \\ 
            \textbf{Neurocognitive} & \fseries 7711 \\ 
            \textbf{MCI} & \fseries 3889 \\ 
            \textbf{Amnesia} & \fseries 3695 \\ 
            \textbf{AD} & \fseries 2673 \\ 
            \textbf{Lewy} & \fseries 2561 \\ 
            \textbf{MMSE} & \fseries 2134 \\ 
            \textbf{LBD} & \fseries 224 \\ 
            \textbf{Corticobasal} & \fseries 147 \\ 
            \textbf{Pick's} & \fseries 41 \\

            \bottomrule
        \end{tabular}
    }
\end{table*}

\paragraph{Annotations}
\label{sec:Annotations} We initially assigned 5,000 sequences diversified by keyword matches from 5,000 unique patients for neurologist labeling. As the manual annotation of 279,000+ sequences in not feasible, we devised a scheme to expedite annotations known as "always patterns". An always pattern is defined as a phrase or regex expression that in any context indicates the phrase will be labeled with a particular class (i.e. yes, no, or neither). If an always pattern is inputted, all other sequences have language that matches with the phrase will be automatically labeled accordingly. % {List any other sequence assignment schemes} %
Currently, 8,656 sequences have been annotated, 8,050 through always patterns and 606 manually. % {Will change} %

The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.

\section{Methodology}
\label{sec:Methodology}

We built x models and compared performance to baseline model.

\paragraph{(1) Baseline Model} We performed L1 regularized logistic regression where the cognitive concern label was regressed on the counts of medications and ICD codes relevant to CI. The lambda value was selected through 10-fold Cross Validation (CV) to maximize the average area under the Receiver Operator Characteristic (ROC). % {To be implemented} %

\paragraph{(2) Logistic Regression with TF-IDF Vectors} We performed TF-IDF (term frequency-inverse document frequency) vectorization on the annotated sequences and selected features based on a term's Pearson correlation coefficient with the outcome. L1 Regularized logistic regression was applied with the annotated cognitive impairment labels. We used different correlation coefficients as thresholds to select features and iterated over different lambda values to determine the optimal lambda value and correlation coefficient threshold.

\paragraph{(3) Model 1 + Model 2} % {TBD} %

\paragraph{(4) Transformer Based Sequence Classification Language Model} % {To be implemented} %
